\chapter*{General Conclusion}
\addcontentsline{toc}{chapter}{General Conclusion}

This internship project marked the culmination of my academic journey in Business Intelligence and offered a valuable opportunity to apply both technical and analytical skills in a practical setting. Throughout the development of the POS system, I was able to explore full-stack web technologies, agile project management, and decision-support integration — all within the scope of a real-world application.

The initial phase of the project allowed me to analyze business needs, define clear requirements, and plan technical architecture using tools like UML and Scrum methodology. Each sprint was structured to address a specific feature of the system, and with each iteration, I gained more insight into planning, building, and validating a scalable web application.

Among the key achievements were:
\begin{itemize}
  \item A dual authentication system: Auth0 for admin users and local authentication for cashiers with role-based routing
  \item A functional and responsive POS interface for cashiers
  \item Automatic invoice generation with real-time stock updates
  \item Embedded Power BI dashboards for business analytics
\end{itemize}

Working remotely with Synthron Lab allowed me to develop independently while following professional standards. I learned how to manage time effectively, test iteratively, and produce reliable and readable code. I also experienced the value of structured documentation and sprint-based development in keeping complex projects under control.

While the application is already functional and complete in its current form, several improvements can be explored in future versions.

\section*{Future Enhancements}

\begin{itemize}
  \item Add multi-store and multi-cashier support for larger retail networks.
  \item Integrate barcode scanning for faster item lookup.
  \item Implement offline mode with local caching and sync.
  \item Connect with payment APIs for real-time transaction validation.
  \item Expand BI dashboards to include predictive metrics and export options.
\end{itemize}
