\chapter*{Glossary}
\addcontentsline{toc}{chapter}{Glossary}

This glossary defines key technical terms, acronyms, and tools referenced throughout the report.

\vspace{1em}

\begin{description}

  \item[API] Application Programming Interface – A set of rules that allow different software components to communicate with each other.

  \item[Auth0] A secure OAuth authentication service used specifically for admin user login, sessions, and role-based access control. The system also implements local authentication for cashier users.

  \item[Backlog] A prioritized list of tasks or features to be implemented in upcoming sprints during agile development.

  \item[BI (Business Intelligence)] Technologies and practices for analyzing business data and presenting actionable insights through dashboards and reports.

  \item[Cart System] The interface logic that manages product selection, quantity, and totals during a transaction in the POS.

  \item[Dashboard] A visual interface that displays key performance indicators, statistics, and analytics for decision-making.

  \item[JWT] JSON Web Token – A compact and secure format for transmitting identity and session information between parties.

  \item[Next.js] A full-stack React framework used in the project to handle frontend rendering and backend API routing.

  \item[PDF Invoice] A downloadable document generated after a sale, containing transaction details and a QR code for tracking.

  \item[PlantUML] A text-based diagram tool used to create UML diagrams such as class, sequence, and use case diagrams.

  \item[POS (Point of Sale)] The system used to complete sales transactions, manage inventory, and generate invoices in retail environments.

  \item[PostgreSQL] A relational database system used to store structured data such as users, products, stock levels, and transactions.

  \item[Power BI] A Microsoft business analytics tool used in this project to visualize and embed real-time sales and performance dashboards.

  \item[QR Code] A machine-readable code used in the invoices for referencing the transaction or verifying it later.

  \item[React] A JavaScript library for building user interfaces using reusable components.

  \item[Scrum] An agile framework used to manage project development in iterative sprints with a focus on collaboration and incremental delivery.

  \item[Sprint] A short, time-boxed period (typically one week) in Scrum used to deliver a specific, functional increment of the project.

  \item[Tailwind CSS] A utility-first CSS framework used for styling the POS interface with speed and consistency.

  \item[UML] Unified Modeling Language – A set of standardized diagrams used to model the structure and behavior of a system.

  \item[VS Code] Visual Studio Code – The integrated development environment used for writing and debugging the application code.

\end{description}
